Check integrated kernel convergence

### 2022-10-27 src/0_check_ik-converge/ik-converge.Rmd
Polish ik-convergence

---
title: "Check integrated kernel convergence"
author: "Adam Howes"
output: html_document
---

```{r}
#' Checking the convergence of the integrated kernel as a function of number of samples per area

type <- "random"
L <- 200
grid <- readRDS("depends/grid.rds")
n <- nrow(grid)
samples <- sf::st_sample(grid, type = type, exact = TRUE, size = rep(L, n))
length(samples) # n * L
sf::st_crs(samples) <- NA

#' Add id column
samples <- st_sf(id = rep(seq_along(1:L), n), geom = samples)

sample_sets <- lapply(seq(10, L, by = 10), function(i) subset(samples, id <= i))

# Checking that the samples look OK
cowplot::plot_grid(
  plot_samples(sample_sets[[1]]),
  plot_samples(sample_sets[[10]]),
  plot_samples(sample_sets[[20]]),
  ncol = 3
)

#' Calculate the Gram matrices
covs <- lapply(sample_sets, adapted_integrated_covariance)

@@

matrix_comparison <- outer(covs, covs, Vectorize(frobenius))
plot_matrix(matrix_comparison)

#' Experiment: 10, 20 and 50 points versus ground truth 300 points
L_settings <- list(10, 20, 50)
gt_samples <- sf::st_sample(grid, type = type, exact = TRUE, size = rep(300, n))
gt_cov <- adapted_integrated_covariance(gt_samples)
result <- lapply(L_settings, int_convergence_experiment)

@@

>>>>

---
title: "Check integrated kernel convergence"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Task** We check how the convergence of the integrated kernel varies as a function of number of samples per area.
---

# Performing the check

```{r}
type <- "random"
L <- 200
grid <- readRDS("depends/grid.rds")
n <- nrow(grid)
samples <- sf::st_sample(grid, type = type, exact = TRUE, size = rep(L, n))
length(samples) # n * L
sf::st_crs(samples) <- NA
```

Add an `id` column:

```{r}
samples <- st_sf(id = rep(seq_along(1:L), n), geom = samples)

sample_sets <- lapply(seq(10, L, by = 10), function(i) subset(samples, id <= i))
```

Check that the samples look OK:

```{r}
cowplot::plot_grid(
  plot_samples(sample_sets[[1]]),
  plot_samples(sample_sets[[10]]),
  plot_samples(sample_sets[[20]]),
  ncol = 3
)
```

Calculate the Gram matrices:

```{r}
covs <- lapply(sample_sets, adapted_integrated_covariance)

@@

matrix_comparison <- outer(covs, covs, Vectorize(frobenius))
plot_matrix(matrix_comparison)
```

Perform an experiment with 10, 20 and 50 points versus ground truth 300 points:

```{r}
L_settings <- list(10, 20, 50)
gt_samples <- sf::st_sample(grid, type = type, exact = TRUE, size = rep(300, n))
gt_cov <- adapted_integrated_covariance(gt_samples)
result <- lapply(L_settings, int_convergence_experiment)

@@

# `functions.R`

```{r, echo=TRUE, eval=FALSE, code=readLines('functions.R')}
```

# Original computing environment

```{r}
sessionInfo()
```
